cardinalR: Generating interesting high-dimensional data structures

### 2025-06-24 paper-cardinalR.tex
Add subsections

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

\paragraph{\texorpdfstring{\texttt{gen\_expbranches()}}{gen\_expbranches()}}\label{gen_expbranches}

@@

\paragraph{\texorpdfstring{\texttt{gen\_linearbranches()}}{gen\_linearbranches()}}\label{gen_linearbranches}

@@

\paragraph{\texorpdfstring{\texttt{gen\_curvybranches()}}{gen\_curvybranches()}}\label{gen_curvybranches}

@@

\paragraph{\texorpdfstring{\texttt{gen\_orglinearbranches()}}{gen\_orglinearbranches()}}\label{gen_orglinearbranches}

@@

\paragraph{\texorpdfstring{\texttt{gen\_orgcurvybranches()}}{gen\_orgcurvybranches()}}\label{gen_orgcurvybranches}

@@

\paragraph{\texorpdfstring{\texttt{gen\_gridcube()}}{gen\_gridcube()}}\label{gen_gridcube}

@@

\paragraph{\texorpdfstring{\texttt{gen\_unifcube()}}{gen\_unifcube()}}\label{gen_unifcube}

@@

\paragraph{\texorpdfstring{\texttt{gen\_cubehole()}}{gen\_cubehole()}}\label{gen_cubehole}

@@

\paragraph{\texorpdfstring{\texttt{gen\_quadratic()}}{gen\_quadratic()}}\label{gen_quadratic}

@@

\paragraph{\texorpdfstring{\texttt{gen\_cubic()}}{gen\_cubic()}}\label{gen_cubic}

@@

\paragraph{\texorpdfstring{\texttt{gen\_pyrrect()}}{gen\_pyrrect()}}\label{gen_pyrrect}

@@

\paragraph{\texorpdfstring{\texttt{gen\_pyrtri()}}{gen\_pyrtri()}}\label{gen_pyrtri}

@@

\paragraph{\texorpdfstring{\texttt{gen\_pyrstar()}}{gen\_pyrstar()}}\label{gen_pyrstar}

@@

\paragraph{\texorpdfstring{\texttt{gen\_pyrholes()}}{gen\_pyrholes()}}\label{gen_pyrholes}

@@

\paragraph{\texorpdfstring{\texttt{gen\_scurve()}}{gen\_scurve()}}\label{gen_scurve}

@@

\paragraph{\texorpdfstring{\texttt{gen\_scurvehole()}}{gen\_scurvehole()}}\label{gen_scurvehole}

@@

\paragraph{\texorpdfstring{\texttt{gen\_circle()}}{gen\_circle()}}\label{gen_circle}

@@

\paragraph{\texorpdfstring{\texttt{gen\_curvycycle()}}{gen\_curvycycle()}}\label{gen_curvycycle}

@@

\paragraph{\texorpdfstring{\texttt{gen\_unifsphere()}}{gen\_unifsphere()}}\label{gen_unifsphere}

@@

\paragraph{\texorpdfstring{\texttt{gen\_gridedsphere()}}{gen\_gridedsphere()}}\label{gen_gridedsphere}

@@

\paragraph{\texorpdfstring{\texttt{gen\_clusteredspheres()}}{gen\_clusteredspheres()}}\label{gen_clusteredspheres}

@@

\paragraph{\texorpdfstring{\texttt{gen\_hemisphere()}}{gen\_hemisphere()}}\label{gen_hemisphere}

@@

\paragraph{\texorpdfstring{\texttt{gen\_crescent()}}{gen\_crescent()}}\label{gen_crescent}

@@

\paragraph{\texorpdfstring{\texttt{gen\_curvycylinder()}}{gen\_curvycylinder()}}\label{gen_curvycylinder}

@@

\paragraph{\texorpdfstring{\texttt{gen\_sphericalspiral()}}{gen\_sphericalspiral()}}\label{gen_sphericalspiral}

@@

\paragraph{\texorpdfstring{\texttt{gen\_helicalspiral()}}{gen\_helicalspiral()}}\label{gen_helicalspiral}

@@

\paragraph{\texorpdfstring{\texttt{gen\_conicspiral()}}{gen\_conicspiral()}}\label{gen_conicspiral}

@@

\paragraph{\texorpdfstring{\texttt{gen\_nonlinear()}}{gen\_nonlinear()}}\label{gen_nonlinear}
